\hfill ~\\[-30mm] \phantom{h} \hfill\mbox{\small pre-print number if any?} \\[1cm] \vspace{13mm} \textbf{Precise predictions for same sign W-bosons scattering at the LHC}

### 2017-11-14 Draft/article.tex
Add package `lmodern` for nicer fonts
Update article.tex
changes in the scan and draft

%% Main-Version Draft
\documentclass[11pt,epsf]{article}
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage
 [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
 {subcaption}

@@

\date{}
\author{
Ansgar Denner$^{1\,}$,
Stefan Dittmaier$^{2\,}$,
Michele Grossi$^{3\,}$,
Alexander Karlberg$^{4\,}$, \\
Mathieu Pellen$^{1\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{5\,}$,
Michael Rauch$^{6\,}$,
J\"urgen Reuter$^{7\,}$,
Vincent Rothe$^{7\,}$, \\
Christopher Schwan$^{2\,}$,
Pascal Stienemeier$^{7\,}$,
Marco Zaro$^{8\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^2${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^3$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^4$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
{\small\it
$^5$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^6$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT), 
,} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^7$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^8$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        }

>>>>

%% Main-Version Draft
\documentclass[11pt,epsf]{article}
%% -------------------------------
%% |          Packages           |
%% -------------------------------
 \usepackage{amsmath}
 \usepackage{graphicx}
 \usepackage[merge,numbers,compress]{natbib}
 \usepackage[T1]{fontenc}
 \usepackage{booktabs}
 \usepackage{xcolor} 
 \usepackage{xspace}
 \usepackage{dcolumn}
 \usepackage{hyperref}
 \usepackage{caption}
 \usepackage{tabularx}
 \usepackage{lmodern}
 \usepackage
 [subrefformat=parens,position=top,skip=-15pt,margin=15pt,justification=justified,singlelinecheck=false]
 {subcaption}

@@

\date{}
\author{
Simon Brass$^{1\,}$,
Ansgar Denner$^{2\,}$,
Stefan Dittmaier$^{3\,}$,
Michele Grossi$^{4\,}$, \\
Alexander Karlberg$^{5\,}$, 
Mathieu Pellen$^{2\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{6\,}$,
Michael Rauch$^{7\,}$,
J\"urgen Reuter$^{8\,}$, \\
Vincent Rothe$^{8\,}$, 
Christopher Schwan$^{3\,}$,
Pascal Stienemeier$^{8\,}$,
Marco Zaro$^{9\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at Siegen, Department Physik,} \\ %
{\small\it Walter-Flex-Str.3, \linebreak %
        57068 Siegen, Germany}\\[3mm]
        %
{\small\it
$^2$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^3${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^4$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^5$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
{\small\it
$^6$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^7$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT),} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^8$DESY Theory Group,} \\ %
{\small\it Notkestr. 85, \linebreak %
        D-22607 Hamburg, Germany}\\[3mm]
        %
{\small\it
$^9$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        }
